\begin{experienceSection}{Professional Experience}
    %
    \experienceItem[
        company={NYC Department of Design and Construction},
        location={New York, NY},
        position={Service Desk Technician},
        duration={July 2026 – Present}
    ]
    
    \experienceItem[
        company={NASA New York Space Grant Consortium},
        location={New York, NY},
        position={Machine Learning Researcher},
        duration={Jan 2026 – May 2026}
    ]
    \begin{itemize}
        \itemsep -6pt {}
        \item Built 4+ binary MBTI personality models trained on a dataset of 112K+ social media posts, achieving a 91\% precision-recall.
        \item Deployed an end-to-end system including a reverse proxy, a WSGI server and a web application via 2+ Docker containers.
        \item Trained 2+ computer vision models to recognize handwritten digits and the alphabet, reaching 86\% and 89\% accuracy.
    \end{itemize}
    
    \experienceItem[
        company={NYC Department of Social Services},
        location={New York, NY},
        position={Cybersecurity Intern},
        duration={March 2026 – April 2026}
    ]
    \begin{itemize}
        \itemsep -6pt {}
        \item Audited account name duplicates weekly from 5K-record Excel datasets via 8+ functions with wildcards to match name typos.
        \item Developed a Python MCP server that exposes 1+ tool to a local AI chatbot built with Open WebUI and the Ollama service.
        \item Deployed a local AI chatbot and an MCP server application using 3+ Docker containers defined in a docker-compose file. 
        % \item Still working on this...
        % \item Still working on this...
    \end{itemize}

    %%% 
    \experienceItem[
        company={Queensborough Community College},
        location={Bayside, NY},
        position={Undergraduate Research Scholar},
        duration={September 2025 – May 2026}
    ]
    \begin{itemize}
        \itemsep -6pt {}
        \item Deployed a network-based IDPS using the Snort3 and Suricata engines in a virtual network of 3+ clients built with QEMU/KVM.
        \item Simulated 29+ transmissions containing infected traffic to compare alerts and memory performance between both engines.
        \item Found that Suricata performed at a 65\% precision against traffic containing Lumma Stealer signatures while Snort3 a 33\%.
    \end{itemize}
%
% \vspace{-0.5em}%
% \positionItem[
%     position={Peer Tutor},
%     duration={January 2026 - March 2026}
%     ]
%     \begin{itemize}
%         \itemsep -6pt {}
%         \item Still working on this...
%         \item Still working on this...
%         \item Still working on this...
%     \end{itemize}
% %
% \vspace{-0.5em}%
% \positionItem[
%     position={Office Assistant Intern},
%     duration={October 2025 - December 2025}
%     ]
%     \begin{itemize}
%         \itemsep -6pt {}
%         \item Managed data entry for 132+ program participants across Google Sheets, ensuring PII compliance and accurate reporting.
%         \item Executed an outreach campaign of 60+ calls to participants, significantly increasing end-of-semester survey completion rates.
%         \item Conducted inventory counts and organization of 182+ program supplies to optimize office space and resource accessibility.
%     \end{itemize}

\end{experienceSection}